R Notebook

### 2018-09-13 article_code.Rmd
title
Comments

---
title: "R Notebook"
output: html_notebook
---

# the project is in Dropbox/coding/cosimulation

```{r}
source("C:/Users/tl3315/Dropbox/coding/cosimulation/co_sim_condi.R")
source("C:/Users/tl3315/Dropbox/coding/cosimulation/cosim_functions.R")
```
```{r}
library(mvtnorm)
library(abind)
```

>>>>

---
title: "R Notebook"
output: html_notebook
---
# Simulation of the Latemar Carbonate platform

loading the functions, replace with the location of your files
```{r}
source("C:/Users/tl3315/Dropbox/coding/cosimulation/co_sim_condi.R")
source("C:/Users/tl3315/Dropbox/coding/cosimulation/cosim_functions.R")
```
Two libraries used that you first need to install with R
mvtnorm compute integral over Gaussian densities
```{r}
library(mvtnorm)
library(abind)
```
